Radio Emission from Red-Giant Hot Jupiters

### 2015-12-28 ms.tex
Minor change -- put sentence on its own line.
revision of the last part of section 2, plus minor edits

\revise{In reality, only the neutral portion of the stellar wind can accrete onto the planet without interacting with planetary magnetic field and thus Bondi-Hoyle accretion would be relevant. 
The ionized portion could lose some of their energy at the bow shock before they accrete, and energy released there is less than the estimate by equations (\ref{eq:Lacc}) and (\ref{eq:Tacc}). 
%Now the stellar wind is so dense that the mean free path is comparable to the Jovian radius, the neutral and ionized particles may also drag each other. 
%While interacting with magnetic field, the ionized portion could lose their energy 
%Therefore, some part of the incoming wind particles are what we could envision is the 
%Considering other uncertainties of radio wave generation, we 
The detailed electromagnetic structure around RGHJs therefore requires  elaborate numerical simulations, which is beyond the scope of this paper. Noting these uncertainties, in this paper we simply aim to give an order-of-magnitude estimate. }

@@

\revise{%
Once planetary radio emission is detected, it in general provides a unique approach for learning the planetary property. As the auroral radio flux is significantly modulated in association with several physical processes described in \S\ref{ss:timevariability}, the time variability is useful to imply the planetary spin rotation period or the presence of satellites. If spectra are obtained, the upper cut-off frequency can tell us the magnetic field strength of the planetary surfaces, which, when combined with constrains on the planetary mass via e.g. radial-velocity observations, tests  the proposed scaling law of planetary dynamo. 
Furthermore, the lower cut-off frequency of the RGHJ emission, which presumably corresponds to in situ plasma frequency, could probe the stellar wind property at the planetary orbit. In addition, the planetary radio power in such an extreme environment as RG's massive stellar wind will be valuable data points to test the empirical ``radiometric Bode's law''. %
We also note that the radio emission of RGHJs may also be used as a tool for discovering/confirming new planets, given that traditional exoplanet-discovery methods (specifically, transit and radial-velocity observations) are not very sensitive to planets around RGB or AGB stars. %
}

>>>>

\revise{In reality, the temperature and luminosity based on the Bondi-Hoyle accretion (Eq. (\ref{eq:Lacc} and (\ref{eq:Tacc}) describes the situation only approximately. Precisely, only the neutral portion of the stellar wind can accrete onto the planet without interacting with planetary magnetic field, and the ionized portion would lose some energy at the bow shock before it accretes. On the other hand, the ionized plasmas interacting with magnetic field could have a cross section larger than the Bondi–Hoyle accretion radius. The detailed electromagnetic structure around RGHJs therefore requires elaborate numerical simulations, which is beyond the scope of this paper. Noting these uncertainties, in this paper we simply aim to give an order-of-magnitude estimate. }

@@

\revise{%
Once planetary radio emission is detected, it provides a unique approach for learning the planetary property. As the auroral radio flux is significantly modulated in association with several physical processes described in \S\ref{ss:timevariability}, the time variability is useful to imply the planetary spin rotation period or the presence of satellites. If spectra are obtained, the upper cut-off frequency can tell us the magnetic field strength of the planetary surfaces, which, when combined with constrains on the planetary mass via e.g. radial-velocity observations, tests  the proposed scaling law of planetary dynamo. 
Furthermore, the lower cut-off frequency of the RGHJ emission, which presumably corresponds to in situ plasma frequency, probes the stellar wind properties at the planetary orbit. In addition, the planetary radio power in such an extreme environment as a RG's massive stellar wind will be valuable data points to test the empirical ``radiometric Bode's law''. %
We also note that the radio emission of RGHJs may also be used as a tool for discovering/confirming new planets, given that traditional exoplanet-discovery methods (specifically, transit and radial-velocity observations) are not very sensitive to planets around RGB or AGB stars. %
}
